\frameT{Computational and Data-Driven Research on Preferences}{
	\begin{enumerate}
		\item Submit proposals to NSF (esp. CISE/IIS), DUE, DARPA, ARPA-E, among other possibilities.
		\item Data: binary vs. graded, absolute vs. relative, explicit vs. implicit,
					structured vs. unstructured, and single vs. multiple users.
			\begin{itemize}
				\item Construct datasets using data mining and filtering techiques.
				\item Tools: Bash, Python, and Matlab.
			\end{itemize}
		\item Methods/Models: recommender systems, supervised learning, conditional preference
					networks, and preference trees.
			\begin{itemize}
				\item Familiarize with related literature, design and implement new preference
							representations.
				\item Collaboration within the department and with the Department of Mathematics.
				\item Tools: C/C++, logic programming solvers, and Matlab.
			\end{itemize}
		\seti
	\end{enumerate}
}

\frameT{Computational and Data-Driven Research on Preferences}{
	\begin{enumerate}
		\conti
		\item Behavioral research:
			\begin{itemize}
				\item Design and implement research involving human participants through CofC IRB.
				\item Collaboration with the School of Humanities and Social Sciences.
			\end{itemize}
		\item Reasoning tasks: dominance and optimization, and preference aggregation.
			\begin{itemize}
				\item Implement decision support systems.
				\item Tools: C/C++, logic programming solvers, SAT solvers, and Matlab.
			\end{itemize}
		\item Applications: fair division, strategyproof social choice, and planning and scheduling.
			\begin{itemize}
				\item Prove computational complexities.
				\item Design and implement approximation algorithms.
				\item Tools: C/C++, logic programming solvers, and SAT solvers.
			\end{itemize}
	\end{enumerate}
}
